Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-13 paper/paper.tex
questions

Figure 1. Summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the
multiphase model (thick line)  and the rotating homogeneous gas sphere
(thin line).

The fit to the observations is not perfect. 
However, in spite of the
simplicity of our models, this is the first time that the main
\tol\ features can be reproduced: a broad, highly symmetric,
single-peaked \lya line.

@@

From the K-S tests we confirm that only 3 parameters 
can be constrained by observations;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
This does not mean the other parameters do not influence the resulting
spectra at all; it means that they cannot be constrained from \tol's
observations.

@@

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile represents
the kinematics of the clumps, that is, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty}$ \& $\beta_{\rm cl}$. 
Furthermore, the relatively low mean number of clumps per line of
sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion
of the clumps implies the  existence of low-density inter-clump 
regions where \lya photons can freely propagate which leads to an
emergent spectrum close to the intrinsic one as well as to the high
flux at line center as observed. 
Because the width of the observable spectrum is hence set primarily by
$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
narrower line and thus a worse fit. 
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is we have a $30\%$ chance to find good models compared with the
lower $1\%$ success rate if the parameters were unconstrained. 
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $1\sigma$. All the other parameters were unconstrained.}

Having constrained only 3 parameters one might wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading because merely the best-fit values of
(some of) those $3$ parameters, i.e., the corresponding constraint to
a given sub-region in the parameter space, make the other parameters
less important. 
For instance, in our case the large value of $P_{\rm cl}$ makes
radiative transfer effects, and therefore other parameters such as the
clump column density less relevant for the emergent line
profile. However, for instance larger values of $f_{\rm cl}$ --
outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected,
\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
i.e. we cannot randomly pick 11 random values for these
parameters and expect to fit the line profile while only varying the
other 3

We cannot discard that another region of parameter space
could also yield a good fit to the observed line-profile.
This might be interesting to explore in the
future with, e.g., a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol \footnote{In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.}.

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the rotational
velocity of $\sim350$ \kms\ is too high for such a low
mass system.  \mg{I am confused -- are much lower rotational velocities not exclude by the priors used?}
\tol's inferred rotational velocity is larger than the
Milky Way's ($\sim200$\kms) while its baryonic mass is one order
of magnitude smaller. 
Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

>>>>

Figure 1. Summarizes our main finding.
Dots represent the observational data for \tol\ with the
overplot from our best fits from the analytical solution for the
multiphase model (thick line)  and the rotating homogeneous gas sphere
(thin line). 
The fit to the observations is not perfect. 
However, in spite of the
simplicity of our models, this is the first time that the main
\tol\ features can be reproduced: a broad, highly symmetric,
single-peaked \lya line.

@@

From the K-S tests we confirm that only 3 parameters 
can be constrained by observations;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
All the other parameters cannot be constrained from \tol's
observations.

@@

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile represents
the kinematics of the clumps, that is, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ \& $\beta_{\rm cl}$. 
Furthermore, the relatively low mean number of clumps per line of
sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion
of the clumps implies the  existence of low-density inter-clump 
regions where \lya photons can freely propagate which leads to an
emergent spectrum close to the intrinsic one as well as to the high
flux at line center as observed. 
Because the width of the observable spectrum is hence set primarily by
$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
narrower line and thus a worse fit. 
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$\kms.

As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is, we have a $30\%$ chance to find good models, which is
significanty higher than the lower $1\%$ success rate if the
parameters were unconstrained.  
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $3\sigma$. All the other parameters,
  including $v_{\infty}$were
  unconstrained.}

Having constrained only 3 parameters one might wonder why the other 11
parameters do not seem to matter.
In our case this can be explained by the large value of $P_{\rm cl}$
favored by \tol's observations. 
A large proability of having \lya\ photons emitted in the clumps
makes radiative transfer effects, and therefore other parameters such
as the clump column density, less relevant for the emergent line
profile.

\jefr{I find this paragraph confusing. Discussing an hypotetical case where
all parameters matter undermines the explanation of our concrete case
where only some parameters matter more. Probably we can remove it}.
{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected.}

However, we cannot discard that another region of parameter space
could also yield a good fit to the observed line-profile.
This might be interesting to explore in the
future with, e.g., a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol.In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the rotational
velocity of $\sim350$ \kms\ is too high for such a low
mass system.  \mg{I am confused -- are much lower rotational
  velocities not exclude by the priors used?}\jefr{Yes, they are
  discarded, but here we are talking about the most likely value of
  350 km/s.}
\tol's inferred rotational velocity is larger than the
Milky Way's ($\sim200$\kms) while its baryonic mass is one order
of magnitude smaller. 
Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.
